Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-05-25 props.tex
Cleaned up notation on props.tex and put it in a two-column form

\documentclass{article}

@@

@@

    A policy tracks a mix of static and dynamic enforcement. A policy consists of
    a set of policy states, \(p \in \mathcal{P}\), a policy initializer
    \(pinit : \mathcal{M} \rightharpoonup \mathcal{P}\), and a policy-parameterized step function:
    \[m, p \xrightarrow{o}_P m', p' : m \in \mathcal{M} \times p \in \mathcal{P} \rightharpoonup
    o \in \mathit{Obs} \times m' \in \mathcal{M} \times p' \in \mathcal{P}\]

@@

    A machine trace \(M\) is a sequence of machine states \(m_0 m_1 m_2 \dots\) such that each
    pair of adjacent states are related by \(\longrightarrow\) with some observation. An
    {\it mptrace} is similarly a sequence of machine state-policy state pairs,
    \((m_0,\mathit{pinit}(m_0))(m_1,p_1) \dots\) such that adjacent pairs of pairs are related
    by \(\longrightarrow_P\). Steps being deterministic, we can relate an initial state to its trace
    via \(\cdot \hookrightarrow \cdot : \mathcal{M} \rightarrow \mathit{trace}\ \mathcal{M}\):

@@

    Since the step function is total, if \(m \hookrightarrow M\), then \(M\) must be infinite.
    We will also wish to take a prefix of the trace from an initial state up to when some condition
    holds. Let \(f\) be a predicate on machine states. Then we define \(m \hookrightarrow M | f\)
    (read ``\(M\) is the prefix from \(m\) until \(f\)'') by:

    \begin{minipage}[b]{.45\textwidth}
      \[\frac{m_0 \xrightarrow{o} m_1 \hspace{.5cm} \neg f\ m_1 \hspace{.5cm} m_1 \hookrightarrow M | f }
             {m_0 \hookrightarrow m_0 M | f}\]
    \end{minipage}
    \begin{minipage}[b]{.45\textwidth}
      \[\frac{m_0 \xrightarrow{o} m_1 \hspace{.5cm} f\ m_1}
             {m_0 \hookrightarrow m_0 m_1}\]
    \end{minipage}
    \vspace{\belowdisplayskip}

    We similarly define \(\hookrightarrow_P\), writing \(m_0,\mathit{pinit}(m_0) \longrightarrow \bot\) when
    there is no \(m_1,p_1\) such that \(m_0,\mathit{pinit}(m_0) \xrightarrow{o} m_1,p_1\) for any \(o\).

    \begin{minipage}[b]{.45\textwidth}
      \[\frac{m_0,p_0 \xrightarrow{o} m_1,p_1 \hspace{.5cm} m_1,p_1 \hookrightarrow_P MP}
             {m_0,p_0 \hookrightarrow_P m_0,p_0 MP}\]
    \end{minipage}
    \begin{minipage}[b]{.45\textwidth}
      \[\frac{m_0,p_0 \longrightarrow \bot}
             {m_0,p_0 \hookrightarrow_P m_0,p_0}\]
    \end{minipage}
    \vspace{\belowdisplayskip}

    With a policy we may see \(m,p \hookrightarrow MP\) where \(MP\) is finite due to a policy
    failure. We will identify the set of infinite traces as \(\top\), so \(MP \in \top\) will
    indicate an infinite trace and \(MP \not \in \top\) a finite one.
    We define a similar notion of taking the prefix until a condition:

    \begin{minipage}[b]{.45\textwidth}
      \[\frac{m_0,p_0 \xrightarrow{o} m_1,p_1 \hspace{.5cm} \neg f\ m_1 \hspace{.5cm} m_1,p_1
                \hookrightarrow_P M | f }
             {m_0,p_0 \hookrightarrow_P m_0,p_0 M | f}\]
    \end{minipage}
    \begin{minipage}[b]{.45\textwidth}
      \[\frac{m_0,p_0 \xrightarrow{o} m_1,p_1 \hspace{.5cm} f\ m_1}
             {m_0,p_0 \hookrightarrow_P (m_0,p_0) (m_1,p_1)}\]
    \end{minipage}
    \vspace{\belowdisplayskip}

    An observation trace \(O\) is the trace of observations from a machine or {\it mptrace},
    as defined by \(\mathit{ObsOf}\):

    \begin{minipage}[b]{.45\textwidth}
      \[\frac{M = mM' \hspace{.5cm} m \xrightarrow{o} m' \hspace{.5cm} \mathit{ObsOf}(M') = O}
             {\mathit{ObsOf}(M) = oO}\]
    \end{minipage}
    \begin{minipage}[b]{.45\textwidth}
      \[\frac{M = m}
             {\mathit{ObsOf}(M) = \tau}\]
    \end{minipage}
    \vspace{\belowdisplayskip}

    \begin{minipage}[b]{.45\textwidth}
      \[\frac{MP = (m,p)MP' \hspace{.5cm} m,p \xrightarrow{o} m',p' \hspace{.5cm} \mathit{ObsOf}(MP') = O}
             {\mathit{ObsOf}(MP) = oO}\]
    \end{minipage}
    \begin{minipage}[b]{.45\textwidth}
      \[\frac{MP = m,p}
             {\mathit{ObsOf}(M) = \tau}\]
    \end{minipage}
    \vspace{\belowdisplayskip}

    We abbreviate the observation trace of the execution trace from a state as:
    \[m \rightsquigarrow O \triangleq m \hookrightarrow M \land \mathit{ObsOf}(M) = O\]
    \[m,p \rightsquigarrow O \triangleq m,p \hookrightarrow_P MP \land \mathit{ObsOf}(MP) = O\]

    An observational prefix \(O_1 \lesssim O_2\) means that \(O_1\) is a prefix of \(O_2\) up to the deletion
    of \(\tau\) observations:

    \[O_1 \sim O_2 \triangleq
      \begin{cases}
        O_1' \sim O_2 & \text{if } O_1 = \tau O_1' \\
        O_1 \sim O_2' & \text{if } O_2 = \tau O_2' \\
        O_1' \sim O_2' & \text{if } O_1 = w O_1' \text{ and } O_2 = w O_2' \\
        \text{True} & \text{if for all } o \text{ in } O_1, o = \tau \\
      \end{cases}\]

    Observational equivalence is defined as a symmetric prefix:
    \[O_1 \simeq O_2 \triangleq O_1 \lesssim O_2 \land O_2 \lesssim O_1\]

@@

      \[\frac{m_0,\mathit{pinit}(m_0) \hookrightarrow_P \dots m,p \dots \hspace{.5cm}
              m_0 \hookrightarrow \dots M \dots \hspace{.5cm} \mathit{call}(M) = m, n, a_{pc}, a_{sp}}
             {\mathit{call}_P(m,p) = n, a_{pc}, a_{sp}}\]

      A state is considered to have returned after a call if the stack pointer is the same as before the call
      (\(a_{sp}\)) and the program counter is the next address after (\(a_{pc}\)):
      \[\mathit{returned}\ m\ a_{pc}\ a_{sp} \triangleq m'(\mathtt{SP}) = a_{sp} \land m(\mathtt{PC}) = a_{pc}\]

@@

      \begin{itemize}
        \item Let \(m_0,\mathit{pinit}(m_0) \rightsquigarrow O\) and \(m_0' \rightsquigarrow O'\)
        \item If \(m_0,\mathit{pinit}(m_0) \hookrightarrow_P MP \in \top\) then \(O \simeq O'\)
        \item Otherwise \(O \lesssim O'\)
      \end{itemize}

@@

      When \(m,p\) is a call state \(\mathit{call}_P(m,p) = n,\_,\_\) for some \(n\),
      we can construct a contour based on the size of \(m\)'s stack frame, as follows:
      \[Cof(m,n)(k) =
      \begin{cases}
        (\mathtt{HC},\mathtt{HI}) & \text{if } k \in \mathcal{W}
                                    \text{ and } k \leq m(\mathtt{SP}) - n \\
        (\mathtt{HC},\mathtt{LI}) & \text{if } k \in \mathcal{W}
                                    \text{ and } k \geq m(\mathtt{SP}) \\
        (\mathtt{LC},\mathtt{HI}) & \text{if } k \in \mathcal{W}
                                    \text{ and } k = m(\mathtt{SP}) - 1 \\
        (\mathtt{LC},\mathtt{LI}) & \text{else} \\
      \end{cases}\]

@@

      A system enjoys observable integrity if for any initial state \(m_0\), call state \(m_c\),
      and policy state \(p_c\) such that \(m_0,\mathit{pinit}(m_0) \hookrightarrow \dots (m_c,p_c) \dots\)
      and \(\mathit{call}_P(m_c,p_c) = n,a_{pc},a_{sp}\):

      \begin{itemize}
        \item If \((m_c,p_c) \hookrightarrow \dots (m_r,p_r) | \mathit{returned}\ m_r\ a_{pc}\ a_{sp}\):
          \begin{itemize}
            \item Let \(C = \mathit{Cof}(m_c,n)\)
            \item Let \(m_r' = \mathit{roll}_I(C,m_c,m_r)\), \((m_r,p_r) \rightsquigarrow O\), and
              \(m_r' \rightsquigarrow O'\)
            \item If \(m_r,p_r \hookrightarrow MP \in \top\) then \(O \simeq O'\)
            \item Otherwise \(O \lesssim O'\)
          \end{itemize}
      \end{itemize}

@@

      An eager enforcement mechanism implements a stronger property, which we term {\it eager integrity}.
      Eager integrity simplifies observable integrity by requiring that high integrity data of \(m_r\) be
      identical to that of \(m_c\). Formally, a system enjoys eager integrity if for any initial state
      \(m_0\), call state \(m_c\), and policy state \(p_c\) such that \(\mathit{call}(m_c,p_c) =
      n, a_{pc}, a_{sp}\), and some \(m_r\) and \(p_r\) such that
      \(m_0,\mathit{pinit}(m_0) \hookrightarrow \dots (m_c,p_c) \dots (m_r,p_r) | \mathit{returned}\ m_r\ a_{pc}\ a_{sp}\):

@@

      In this case, a confidentiality rollback takes a contour and four states: two call states
      that will be variants, and two return states. It is not symmetric, regarding \(m_c\) and \(m_r\)
      as the ``real'' call and return, \(m_c'\) as a variant and \(m_r'\) as a return that follows it.

      \[\mathit{roll}_C(C,m_c,m_c',m_r,m_r')(k) =
        \begin{cases}
          m_c(k) & \text{if } C(k) = \mathtt{HC} \text{ and } m_c(k) = m_r(k) \text{ and } m_c'(k) = m_r'(k) \\
          m_r'(k) & \text{else} \\
        \end{cases}\]

      A system enjoys observable confidentiality if for any initial state \(m_0\), call state \(m_c\),
      and policy state \(p_c\) such that \(m_0,\mathit{pinit}(m_0) \hookrightarrow \dots (m_c,p_c) \dots\) and
      \(\mathit{call}(m_c,p_c) = n, a_{pc}, a_{sp}\):

      \begin{itemize}
        \item Let \(C = \mathit{Cof}(m_c,n)\)
        \item For all \(m_c'\) such that \(m_c \approx_C m_c'\):
        \item If \((m_c,p_c) \hookrightarrow MP (m_r,p_r) | \mathit{returned}\ m_r\ a_{pc}\ a_{sp}\)
          \begin{itemize}
            \item Then there is some \(m_r'\) where
              \(m_c' \hookrightarrow M m_r' | \mathit{returned}\ m_r'\ a_{pc}\ a_{sp}\)
            \item Let \(m_r'' = \mathit{roll}_C(C,m_c,m_r,m_c',m_r')\),
              \((m_r,p_r) \rightsquigarrow O\), and \(m_r'' \rightsquigarrow O'\)
            \item If \(m_r,p_r \hookrightarrow_P MP \in \top\) then \(O \simeq \mathit{ObsOf}(M) +\!\!\!+ O'\)
            \item Otherwise \(O \lesssim \mathit{ObsOf}(M) +\!\!\!+ O'\)
          \end{itemize}
        \item Else, let \(m_c,p_c \rightsquigarrow O\) and \(m_c' \rightsquigarrow O'\)
          \begin{itemize}
            \item If \(m_c,p_c \hookrightarrow_P MP \in \top\) then \(O \simeq O'\)
            \item Otherwise \(O \lesssim O'\)
          \end{itemize}
      \end{itemize}

@@

      Once again an eager policy enforces a stronger property that only concerns the behavior of
      the original trace and its variant within each call. A system enjoys {\it eager stack
      confidentiality} if, for any initial state \(m_0\) and call state \(m_c\) such that
      \(m_0,\mathit{pinit}(m_0) \hookrightarrow \dots (m_c,p_c) \dots\) and
      \(\mathit{call}(m_c,p_c) = n, a_{pc}, a_{sp}\):

      \begin{itemize}
        \item Let \(C = \mathit{Cof}(m_c,n)\)
        \item For all \(m_c'\) such that \(m_c \approx_C m_c'\):
        \item If \((m_c,p_c) \hookrightarrow_P MP (m_r,p_r) | \mathit{returned}\ m_r\ a_{pc}\ a_{sp}\)
          \begin{itemize}
            \item Then there is some \(m_r'\) where
              \(m_c' \hookrightarrow M m_r' | \mathit{returned}\ m_c'\ m_r'\)
            \item \(\mathit{ObsOf}(MP) \simeq \mathit{ObsOf}(M)\)
            \item And for all \(k\), if \(m_c(k) \not = m_r(k)\) or \(m_c'(k) \not = m_r'(k)\),
              \(m_r(k) = m_r'(k)\)
          \end{itemize}
        \item Else, let \(m_c,p_c \rightsquigarrow O\) and \(m_c' \rightsquigarrow O'\)
          \begin{itemize}
            \item If \(m_c,p_c \hookrightarrow_P MP \in \top\) then \(O \simeq O'\)
            \item Otherwise \(O \lesssim O'\)
          \end{itemize}
      \end{itemize}

>>>>

\documentclass[conference]{IEEEtran}

@@

\newcommand{\MP}{\mathit{MP}}

@@

    A policy tracks a mix of static and dynamic enforcement. A policy consists of
    a set of policy states, \(p \in \mathcal{P}\), a policy initializer
    \(pinit : \mathcal{M} \rightharpoonup \mathcal{P}\), and a policy-parameterized step function:
    \[\begin{split}
      m, p \xrightarrow{o}_P m', p' : m \in \mathcal{M} \times p \in \mathcal{P} & \rightharpoonup \\
      o \in \mathit{Obs} \times m' \in \mathcal{M} \times p' \in \mathcal{P} &
    \end{split}\]

@@

    A machine trace \(M\) is a sequence of machine states \(m_0 m_1 m_2 \dots\) such that each
    pair of adjacent states are related by \(\longrightarrow\) with some observation. An
    {\it mptrace} is similarly a sequence of machine state-policy state pairs,
    \((m_0,\mathit{pinit}(m_0))(m_1,p_1) \dots\) such that adjacent pairs of pairs are related
    by \(\longrightarrow_P\). Steps being deterministic, we can relate an initial state to its trace
    via \(m \hookrightarrow M : m \in \mathcal{M} \rightarrow M \in \mathit{trace}\ \mathcal{M}\):

@@

    Since the step function is total, if \(m \hookrightarrow M\), then \(M\) must be infinite.
    We will also wish to take a prefix of the trace from an initial state up to when some condition
    holds. Let \(f\) be a predicate on machine states. Then we define \(m \hookrightarrow M | f\)
    (read ``\(M\) is the prefix from \(m\) until \(f\)'') where \(f\) may bind states in \(M\):
    \[\frac{m_0 \xrightarrow{o} m_1 \hspace{.5cm} \neg f\ m_1 \hspace{.5cm} m_1 \hookrightarrow M | f }
           {m_0 \hookrightarrow m_0 M | f}\]
    \[\frac{m_0 \xrightarrow{o} m_1 \hspace{.5cm} f\ m_1}
           {m_0 \hookrightarrow m_0 m_1}\]

    We similarly define \(\hookrightarrow_P\), writing \(m_0,\mathit{pinit}(m_0) \longrightarrow \bot\) when
    there is no \(m_1,p_1\) such that \(m_0,\mathit{pinit}(m_0) \xrightarrow{o} m_1,p_1\) for any \(o\).
    \[\frac{m_0,p_0 \xrightarrow{o} m_1,p_1 \hspace{.5cm} m_1,p_1 \hookrightarrow_P \MP}
           {m_0,p_0 \hookrightarrow_P m_0,p_0 \MP}\]
    \[\frac{m_0,p_0 \longrightarrow \bot}
           {m_0,p_0 \hookrightarrow_P m_0,p_0}\]

    With a policy we may see \(m,p \hookrightarrow \MP\) where \(\MP\) is finite due to a policy
    failure. We will identify the set of infinite traces as \(\top\), so \(\MP \in \top\) will
    indicate an infinite trace and \(\MP \not \in \top\) a finite one.
    We define a similar notion of taking the prefix until a condition:

    \[\frac{m_0,p_0 \xrightarrow{o} m_1,p_1 \hspace{.5cm} \neg f\ m_1 \hspace{.5cm} m_1,p_1
              \hookrightarrow_P M | f }
           {m_0,p_0 \hookrightarrow_P m_0,p_0 M | f}\]
    \[\frac{m_0,p_0 \xrightarrow{o} m_1,p_1 \hspace{.5cm} f\ m_1}
           {m_0,p_0 \hookrightarrow_P (m_0,p_0) (m_1,p_1)}\]

    An observation trace \(O\) is the trace of observations from a machine or {\it mptrace},
    as defined by \(\mathit{Obs}\):
    \[\frac{M = mM' \hspace{.5cm} m \xrightarrow{o} m'}
           {\mathit{Obs}(M) = o\mathit{Obs}(M')}\]
    \[\frac{M = m}
           {\mathit{Obs}(M) = \tau}\]
    \[\frac{\MP = (m,p)\MP' \hspace{.5cm} m,p \xrightarrow{o} m',p'}
           {\mathit{Obs}(\MP) = o \mathit{Obs}(\MP')}\]
    \[\frac{\MP = m,p}
           {\mathit{Obs}(M) = \tau}\]

    An observational prefix \(O_1 \lesssim O_2\) means that \(O_1\) is a prefix of \(O_2\) up to the deletion
    of \(\tau\) observations:
    \[\begin{split}
      O_1 & \sim O_2 \triangleq \forall o . o \in O_1 \Rightarrow o = \tau \lor \\
      & \exists O_1' . O_1 = \tau O_1' \land O_1' \sim O_2 \lor \\
      & \exists O_2' .  O_2 = \tau O_2' \land O_1 \sim O_2' \lor \\
      & \exists O_1' O_2' . O_1 = w O_1' \land O_2 = w O_2' \land O_1' \sim O_2' \\
    \end{split}\]

    Observational equivalence is defined as traces prefixing each other:
    \[O_1 \simeq O_2 \triangleq O_1 \lesssim O_2 \land O_2 \lesssim O_1\]

@@

      \[\frac{\begin{split}
        m_0,\mathit{pinit}(m_0) & \hookrightarrow_P \dots m,p \dots \\ % \hspace{.5cm}
        m_0 & \hookrightarrow \dots M \dots \\
        \mathit{call}(M) & = m, n, a_{pc}, a_{sp}\end{split}}
             {\mathit{call}_P(m,p) = n, a_{pc}, a_{sp}}\]

      A state is considered to have returned after a call if the stack pointer is the same as before the call
      (\(a_{sp}\)) and the program counter is the next address after (\(a_{pc}\)):
      \[\mathit{ret}\ m\ a_{pc}\ a_{sp} \triangleq m(\mathtt{SP}) = a_{sp} \land m(\mathtt{PC}) = a_{pc}\]

@@

      \begin{itemize}
        \item Let \(m_0,\mathit{pinit}(m_0) \hookrightarrow \MP\) and \(m_0' \hookrightarrow M'\)
        \item If \(\MP \in \top\) then \(\mathit{Obs}(\MP) \simeq \mathit{Obs}(M')\)
        \item Otherwise \(\mathit{Obs}(\MP) \lesssim \mathit{Obs}(M')\)
      \end{itemize}

@@

      When \(m,p\) is a call state \(\mathit{call}_P(m,p) = n,\_,\_\) for some \(n\),
      we can construct a contour based on the size of \(m\)'s stack frame, as follows:
      \[\mathit{Cof}(m,n)(k) =
      \begin{cases}
        (\mathtt{HC},\mathtt{HI}) & \text{if } k \leq m(\mathtt{SP}) - n \\
        (\mathtt{HC},\mathtt{LI}) & \text{if } k \geq m(\mathtt{SP}) \\
        (\mathtt{LC},\mathtt{HI}) & \text{if } k = m(\mathtt{SP}) - 1 \\
        (\mathtt{LC},\mathtt{LI}) & \text{else} \\
      \end{cases}\]

@@

      A system enjoys observable integrity as follows:

      For any initial state \(m_0\), call state \(m_c\), and policy state \(p_c\) such that
      \((m_0,\mathit{pinit}(m_0)) \hookrightarrow ... (m_c,p_c) ...\)
      and \(\mathit{call}_P(m_c,p_c) = n,a_{pc},a_{sp}\), if 
      \((m_c,p_c) \hookrightarrow ... (m_r,p_r) | \mathit{ret}\ m_r\ a_{pc}\ a_{sp}\):

          \begin{itemize}
            \item Let \(C = \mathit{Cof}(m_c,n)\)
            \item Let \(m_r' = \mathit{roll}_I(C,m_c,m_r)\), \((m_r,p_r) \hookrightarrow \MP\), and
              \(m_r' \hookrightarrow M'\)
            \item If \(m_r,p_r \hookrightarrow \MP \in \top\) then \(\mathit{Obs}(\MP) \simeq \mathit{Obs}(M')\)
            \item Otherwise \(\mathit{Obs}(\MP) \lesssim \mathit{Obs}(M')\)
          \end{itemize}

@@

      An eager enforcement mechanism implements a stronger property, which we term {\it eager integrity}.
      Eager integrity simplifies observable integrity by requiring that high integrity data of \(m_r\) be
      identical to that of \(m_c\). Formally, a system enjoys eager integrity if for any initial state
      \(m_0\), call state \(m_c\), and policy state \(p_c\) such that \(\mathit{call}(m_c,p_c) =
      n, a_{pc}, a_{sp}\), and some \(m_r\) and \(p_r\) such that
      \(m_0,\mathit{pinit}(m_0) \hookrightarrow ... (m_c,p_c) ... (m_r,p_r) | \mathit{ret}\ m_r\ a_{pc}\ a_{sp}\):

@@

      In this case, a confidentiality rollback takes a contour and four states: two call states
      that will be variants, and two return states. It is not symmetric, regarding \(m_c\) and \(m_r\)
      as the ``real'' call and return, \(m_c'\) as a variant and \(m_r'\) as a return that follows it.
      \[\begin{split}
        & \mathit{roll}_C(C,m_c,m_c',m_r,m_r')(k) = \\
        & \begin{cases}
          m_c(k) & \text{if } C(k) = \mathtt{HC} \text{ and } \\
                  & m_c(k) = m_r(k) \text{ and } m_c'(k) = m_r'(k) \\
          m_r'(k) & \text{else} \\
        \end{cases}
      \end{split}\]

      A system enjoys observable confidentiality as follows:

      For any initial state \(m_0\), call state \(m_c\), and policy state \(p_c\) such that
      \(m_0,\mathit{pinit}(m_0) \hookrightarrow ... (m_c,p_c) ...\) and
      \(\mathit{call}(m_c,p_c) = n, a_{pc}, a_{sp}\):

      \begin{itemize}
        \item Let \(C = \mathit{Cof}(m_c,n)\)
        \item For all \(m_c'\) such that \(m_c \approx_C m_c'\):
        \item If \((m_c,p_c) \hookrightarrow \MP_1 (m_r,p_r) | \mathit{ret}\ m_r\ a_{pc}\ a_{sp}\)
          \begin{itemize}
            \item Then there is some \(m_r'\) where
              \(m_c' \hookrightarrow M_1' m_r' | \mathit{ret}\ m_r'\ a_{pc}\ a_{sp}\)
            \item Let \(m_r'' = \mathit{roll}_C(C,m_c,m_r,m_c',m_r')\),
              \((m_r,p_r) \hookrightarrow \MP_2\), and \(m_r'' \hookrightarrow M_2'\)
            \item If \(\MP \in \top\) then \(\mathit{Obs}(\MP_1) \cdot \mathit{Obs}(\MP_2) \simeq
              \mathit{Obs}(M_1') \cdot \mathit{Obs}(M_2')\)
            \item Otherwise \(\mathit{Obs}(\MP_1) \cdot \mathit{Obs}(\MP_2) \lesssim
              \mathit{Obs}(M_1') \cdot \mathit{Obs}(M_2')\)
          \end{itemize}
        \item Else, for \(\MP\) and \(M'\) such that \(m_c,p_c \hookrightarrow \MP\) and \(m_c' \hookrightarrow M'\):
          \begin{itemize}
            \item If \(\MP \in \top\) then \(\mathit{Obs}(\MP) \simeq \mathit{Obs}(M')\)
            \item Otherwise \(\mathit{Obs}(\MP) \lesssim \mathit{Obs}(M')\)
          \end{itemize}
      \end{itemize}

@@

      Once again an eager policy enforces a stronger property that only concerns the behavior of
      the original trace and its variant within each call. A system enjoys {\it eager stack
      confidentiality} if, for any initial state \(m_0\) and call state \(m_c\) such that
      \(m_0,\mathit{pinit}(m_0) \hookrightarrow ... (m_c,p_c) ...\) and
      \(\mathit{call}(m_c,p_c) = n, a_{pc}, a_{sp}\):

      \begin{itemize}
        \item Let \(C = \mathit{Cof}(m_c,n)\)
        \item For all \(m_c'\) such that \(m_c \approx_C m_c'\):
        \item If \((m_c,p_c) \hookrightarrow_P \MP (m_r,p_r) | \mathit{ret}\ m_r\ a_{pc}\ a_{sp}\)
          \begin{itemize}
            \item Then there is some \(m_r'\) where
              \(m_c' \hookrightarrow M m_r' | \mathit{ret}\ m_c'\ m_r'\)
            \item \(\mathit{Obs}(\MP) \simeq \mathit{Obs}(M)\)
            \item And for all \(k\), if \(m_c(k) \not = m_r(k)\) or \(m_c'(k) \not = m_r'(k)\),
              \(m_r(k) = m_r'(k)\)
          \end{itemize}
        \item Else, for \(\MP\) and \(M'\) such that \(m_c,p_c \hookrightarrow \MP\) and \(m_c' \hookrightarrow M'\)
          \begin{itemize}
            \item If \(\MP \in \top\) then \(\mathit{Obs}(\MP) \simeq \mathit{Obs}(M')\)
            \item Otherwise \(\mathit{Obs}(\MP) \lesssim \mathit{Obs}(M')\)
          \end{itemize}
      \end{itemize}
